---
title: "casestudy2.1"
author: "Uday Allu"
date: "6 March 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#
```{r}
library(datasets)
library(ggplot2)
library(dplyr)
library(plotly)
```

#Read the data
```{r}
Accountopendata<-read.csv(file.choose())
```
#Structure of Data

```{r}
str(Accountopendata)
```



#Summary of Data
```{r}
summary(Accountopendata)
```



#Calculate na values in % 

```{r}
colMeans(is.na(Accountopendata))
```


#Removing NA values
```{r}
Accountopendata<-na.omit(Accountopendata)
```


#Using Plot we can get the relation between the variables.
```{r}
plot(Accountopendata)
```

#Checking the Outlayers
```{r}
boxplot(Accountopendata$Age)
boxplot(Accountopendata$Days.for.decision.after.application)
boxplot(Accountopendata$Days.for.decision.after.lead)
```

#Sampling the data based on Account open Flag
```{r}
Account_flag_1<-Accountopendata%>%filter(Account_open_flag==1)
Account_flag_0<-Accountopendata%>%filter(Account_open_flag==0)
```

#Test data for whether data is normalization or not for Account_flag_1
```{r}
shapiro.test(Account_flag_1$Days.for.decision.after.application)
shapiro.test(Account_flag_1$Days.for.decision.after.lead)
```
# Z-value for Application and lead columns for Account_flag_1
```{r}
Account_flag_1$a_aft_app=scale(Account_flag_1$Days.for.decision.after.application)
Account_flag_1$a_aft_lead=scale(Account_flag_1$Days.for.decision.after.lead)
Account_flag_1
```

#Test data for whether data is normalization or not for Account_flag_0
```{r}
shapiro.test(Account_flag_0$Days.for.decision.after.application)
shapiro.test(Account_flag_0$Days.for.decision.after.lead)

```

# Z-value for Application and lead columns for Account_flag_0
```{r}
Account_flag_0$a_aft_app=scale(Account_flag_0$Days.for.decision.after.application)
Account_flag_0$a_aft_lead=scale(Account_flag_0$Days.for.decision.after.lead)
Account_flag_0
```

#Remove outlayers from data where z value > 3
```{r}
Account_flag_1$a_aft_app<-as.numeric(Account_flag_1$a_aft_app)
Account_flag_1$a_aft_lead<-as.numeric(Account_flag_1$a_aft_lead)
Account_flag_1<-Account_flag_1%>%filter(Account_flag_1$a_aft_app<=3)
Account_flag_0$a_aft_app<-as.numeric(Account_flag_0$a_aft_app)
Account_flag_0$a_aft_lead<-as.numeric(Account_flag_0$a_aft_lead)
Account_flag_0<-Account_flag_0%>%filter(Account_flag_0$a_aft_app<=3)
```


```{r}
shapiro.test(Account_flag_1$a_aft_app)
```

```{r}
shapiro.test(Account_flag_0$a_aft_app)
```


